Assessing Tor's Usability as a Censorship Circumvention Tool

### 2015-05-12 cs261n-paper/paper.tex

\section{UX sprint}
\label{sec:pilot}
\indent \indent This pilot examined the usability of Tor as an anonymity tool
with respect to journalists, a target demographic of users known to use Tor. 
We emphasized the targeting of a high-risk user group of Tor and to 
target usability changes aimed at helping those who could not afford to make mistakes. To see 
if those users had any potentially damaging misunderstandings or incomprehensions of Tor, 
we created tasks to elicit Tor's non-typical behaviors and ask our participants to
navigate through more advanced settings.

@@

We originally had another step after Step~1, ``Configure Tor.''
We removed it after the first two participants
when it became clear that the wording was confusing.
The two main buttons in the configuration wizard are labeled
``Connect'' and ``Configure''; we did not intend for users
to have to go through the longer ``Configure'' path,
but they assumed they had to because of the presence
of the word ``Configure'' in the list of tasks.

@@

\subsection{Methodology} 
\indent \indent We recruited five journalists from Berkeley by reaching out to journalist contacts.
 We recruited five users with an average age of 28 ($\sigma = 13 $~years).  Out of  %?
our five participants, 3 were female.

@@

This pilot was held in conjunction with the first Tor UX sprint. With IRB approval, Tor developers
observed the screens of our participants, which was set to broadcast to a separate  
room during the experiment. Audio of the cognitive walkthrough was not broadcast for privacy
considerations as voice is considered an identifying characteristic.

>>>>

\section{Pilot study}
\label{sec:pilot}
\indent \indent This pilot examined the usability of Tor as an anonymity tool
with respect to journalists, a target demographic of users known to use Tor. 
We emphasized the targeting of a high-risk user group of Tor and to 
target usability changes aimed at helping those who could not afford to make mistakes. To see 
if those users had any potentially damaging misunderstandings or incomprehensions of Tor, 
we created tasks to elicit Tor's non-typical behaviors and ask our participants to
navigate through more advanced settings.

@@

We originally had an extra step after Step~1: ``Configure Tor.''
We removed it after the first two participants
when it became clear that the wording was confusing.
The two main buttons in the configuration wizard are labeled
``Connect'' and ``Configure''; we did not intend for users
to have to go through the longer ``Configure'' path,
but they assumed they had to because of the presence
of the word ``Configure'' in the list of tasks.

@@

\subsection{Methodology} 
\indent \indent We recruited five journalists from the Berkeley area by reaching out to journalist contacts.
 We recruited five users with an average age of 28 ($\sigma = 13 $~years).  Out of  %?
five participants, three were female.

@@

This pilot was held in conjunction with the first Tor UX Sprint. With IRB approval, Tor developers
observed the screens of our participants, which was set to broadcast to a separate  
room during the experiment. Audio of the cognitive walkthrough was not broadcast for privacy
considerations as voice is considered an identifying characteristic.
